Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-13 TACAS2018/paper.tex
more comments
editing sec 6

We are not limited to the synthesis of digital stabilizing controllers -- a
well known task in the literature on digital control systems -- but target
safety requirements with an overall approach that is sound and automated. 
More specifically, we require that the closed-loop system meets given safety
specifications.  A safety specification gives raise to a requirement on the
states of the model, such that the feedback controller (namely the choice of
the gains matrix~$K$) must ensure that the state never violates the
requirement.  Note that a stable, closed-loop system is not necessarily a
safe system: indeed, the state values may leave the safe part of the state
space while they converge to the equilibrium, which is typical in the case
of oscillatory dynamics.  In~this work, the safety property is expressed as:
%
\begin{align}
\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
\label{eq:safetyspec}
\end{align}

@@

In order to synthesize closed-loop digital control systems, we use a program
synthesis engine.  Our program implements Counter-Example Guided
Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
start by presenting its general architecture followed by describing the
parts specific to closed-loop control systems.

CEGIS-based control synthesis requires a formal verifier to check whether a
candidate controller meets the requirements when combined with the plant.
We use the tool Axelerator~\cite{} in the verification module.  It checks the
stability of a cyberphysical closed-loop control system and considers finite-word
length (FWL) effects in the digital controller and continuous dynamics in continuous
time progression in the plant.
As part of the counterexample, Axelerator generates an ANSI-C code model
containing information about different transforms of the system as well as other
abstractions relating to quantization and safety which allow us to create models
for the synthesisers. This specification (which we refer to as $\phi$) is passed to
the Bounded Model Checker CBMC~\cite{ClarkeKL04} which uses SAT solving to
generate a valid input for a controller and observer that meet the given specification.
The ANSI-C code model guarantees that a synthesized solution is complete and
sound with respect to the given abstraction since it does not depend on system
inputs and outputs, but further analysis is required to obatin a solution that meets
the original specification. These results are then fed back to a synthesis module in
Axelerator which uses eigendecomposition and other linear transformations to
refine the solution.

%-------------------------------
\subsection{CEGIS of digital controllers} 
\label{sssec:cegisdig}
%-------------------------------

@@

The benchmark suite employed to evaluate the proposed technique is 
composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}

>>>>

We are not limited to the synthesis of digital stabilizing controllers -- a
well known task in the literature on digital control systems -- but target
safety requirements with an overall approach that is sound and automated. 
More specifically, we require that the closed-loop system meets given safety
specifications.  A safety specification gives raise to a requirement on the
states of the model, such that the feedback controller (namely the choice of
the gains matrix~$K$) must ensure that the state never violates the
requirement.  Note that a stable, closed-loop system is not necessarily a
safe system: indeed, the state values may leave the safe part of the state
space while they converge to the equilibrium, which is typical in the case
of oscillatory dynamics.  In~this work, the safety property is expressed as:
%
\todo{shouldn't this be over the states of the system?}
\begin{align}
\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
\label{eq:safetyspec}
\end{align}

@@

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS. Broadly speaking, CEGIS
denotes an iterative technique where each iteration performs inductive
generalisation based on counterexamples provided by a verification
engine.

%% In order to synthesize closed-loop digital control systems, we use a program
%% synthesis engine.  Our program implements Counter-Example Guided
%% Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
%% start by presenting its general architecture followed by describing the
%% parts specific to closed-loop control systems.

%% CEGIS-based control synthesis requires a formal verifier to check whether a
%% candidate controller meets the requirements when combined with the plant.
%% We use the tool Axelerator~\cite{} in the verification module.  It checks the
%% stability of a cyberphysical closed-loop control system and considers finite-word
%% length (FWL) effects in the digital controller and continuous dynamics in continuous
%% time progression in the plant.
%% As part of the counterexample, Axelerator generates an ANSI-C code model
%% containing information about different transforms of the system as well as other
%% abstractions relating to quantization and safety which allow us to create models
%% for the synthesisers. This specification (which we refer to as $\phi$) is passed to
%% the Bounded Model Checker CBMC~\cite{ClarkeKL04} which uses SAT solving to
%% generate a valid input for a controller and observer that meet the given specification.
%% The ANSI-C code model guarantees that a synthesized solution is complete and
%% sound with respect to the given abstraction since it does not depend on system
%% inputs and outputs, but further analysis is required to obatin a solution that meets
%% the original specification. These results are then fed back to a synthesis module in
%% Axelerator which uses eigendecomposition and other linear transformations to
%% refine the solution.

%% %-------------------------------
%% \subsection{CEGIS of digital controllers} 
%% \label{sssec:cegisdig}
%% %-------------------------------

@@

The benchmark suite employed to evaluate the proposed technique is 
composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.

In the verification module, we use the tool Axelerator~\cite{} .
